% \chapter{Architectural Decisions}\label{ch:overview}

\input{decision-av1}
\newpage
\input{decision-av2}
\newpage
\input{decision-av3}
\newpage
\input{decision-m1}
\newpage
\input{decision-p1}
\newpage
\input{decision-p2}
\newpage
\input{decision-u2}

\section{Other decisions}

    \subsection{Authentication}
        \subsubsection*{KeyDecisions}
            A database is used to store login sessions.

        \subsubsection*{Rationale}
            Authentication is done by verifying user credentials when a user wants to log in. Then a unique session
            is created and the sessionID of this session is returned to the client used by the user. In all subsequent requests,
            the user's client adds this sessionID with the request. If the sessionID exists in the database, then this means
            that the user is still logged in and the request can be handled. Every time the sessionID is checked in the database,
            a timestamp is reset. After a certain time without any requests for this sessionID, the session is deleted from the system. \\

            The \texttt{SessionDB} is used to store all sessions.

        \subsubsection*{Considered Alternatives}
            \paragraph{Files for sessions}
                The sessions could be stored as files on the UserFacade that handlers requests for a user. The facade could then check
                whether or not a certain file exists to check if a user is logged in. However, this would make the facades stateful and
                would add extra overhead in keeping the session files on different nodes consistent with each other in case that the
                user is redirected to another node for load balancing. Keeping different nodes for facades consistent is much easier
                if they are all stateless.

        \subsubsection*{Deployment Decisions}
            The \texttt{SessionDB} is to be deployed on a separate node in order to avoid puttting extra strain on the other databases.
            We expect the SessionDB to receive many more requests than e.g. the \texttt{OtherDataDB}, since users need to send a sessionID
            with every request so that it can be checked whether or not the user is (still) logged in.

    \subsection{Notifications}
        \subsubsection*{KeyDecisions}
            The NotificationHandler stores and sends notifications.

        \subsubsection*{Rationale}
            The \texttt{NotificationHandler} was put in place to deal with
            notifications. Other components can use it to generate notifications for
            certain users in the system. The \texttt{NotificationHandler} will then
            insert information relevant to the notification in the database (message,
            status, date and time, source, ...), and use an external delivery
            service to deliver the notification to users. The used delivery medium
            is based on the user's preferences. The \texttt{DeviceManager} sends request
            to the external delivery service to notifies the
            infrastructure owner, once mote or pluggable device failure occurs.
            Since they are stored in the database, users can always view
            their notifications via their dashboard. \\

        \subsubsection*{Considered Alternatives}
            \paragraph{Custom delivery solution}
                Reliable and quick delivery of notifications is crucial to the
                system in order to solve problems should things go wrong. Currently,
                the solution is to use a third party service for delivery of
                notifications. In the case that no external services are found
                satisfactory, or if this dependency on an external service is
                unwanted, it is possible to build an internal solution for this.
                For example, a \texttt{NotificationSender} component could make use
                of the \texttt{Factory pattern} for different message channels for
                different delivery methods (each with their own sendNotification method).
                This solution allows us to easily add new message channels in the
                future with little effort. The disadvantage of this is that an
                internal solution takes a lot more time to implement.

    \subsection{Application execution subsystem}
        The application execution subsystem is composed of the following components:
        \begin{itemize}
            \item \texttt{ApplicationContainer}
            \item \texttt{ApplicationContainerMonitor}
            \item \texttt{ApplicationContainerManager}
            \item \texttt{ApplicationExecutionSubsystemMonitor}
            \item \texttt{DeviceDataConverter}
            \item \texttt{DeviceCommandConstructor}
        \end{itemize}

        \subsubsection*{Rationale}
            We have designed the application execution subsystem to use the same components on the Online Service and on Gateways,
            because we wanted reuse a lot of functionality in order to make everyones' lives a little easier. This seemed possible to us
            as it seemed to us that in the requirements there was not much different between the application instances running on Gateways
            and on the Online Service. \\
            The biggest difference is that because Gateways are weaker machines than the ones on the Online Service, the applications
            running on the gateways should be of smaller scales. This is perfectly possible by changing some configurations in the
            \texttt{ApplicationContainer}s so that they have stricter limits on the resources used of the node they are running on.
            If an application were to be too large or resource intensive, the \texttt{ApplicationContainerManager}'s 'testApplication' method
            could then generate error messages for the Gateway version of the application.\\
            Furthermore, to make this work smoothly, some interfaces used by the application execution subsystem would need to be
            re-routed to use (the same methods on) different interfaces of different components. For example, the \texttt{DeviceCommandConstructor}
            on the gateway should use the \texttt{DeviceManager} to fetch the correct formatting syntax of a pluggable device, instead of the \texttt{DeviceDB}.
            These things could also be done by using some specific configurations when deploying the components.

\section{Discussion}
    Overall, the architectural decisions lack alternative solutions and alternative deployments decisions.
    More research should be done about different ways to handle the
    non-functional requirements, in order to better judge and compare our solutions.\\

    In retrospect, we should have handled the DeviceDataConverter (and all components which rely on specific pluggable device information) differently.
    If we let data conversion methods be stored on the \texttt{DeviceDB}, we could let the DeviceDataConverter fetch those methods when necessary and maybe
    keep them in some kind of local cache. That way, the new methods can just be added in the database and the component would not need to be re-deployed.
    This is already done with pluggable device information on the \texttt{DeviceManager}; when it detects a new device, it loads information about the device
    and keeps it on the gateway while the device is connected to it.\\

    We should have decomposed the \texttt{DeviceManager} some more to show how device connectivity is being tracked with a \texttt{DeviceMonitor} and how
    applications' device usage/requirements data is stored in a \texttt{ApplicationDataStore}.\\

    Too much communication happens between Gateways and the Online Service, we should have let fewer requests happen between Gateways and the Online Service,
    and do more of the work on a \texttt{GatewayFacade} on the Online Service by doing different method calls from the \texttt{GatewayFacade} instead of \texttt{Gateway}s.

    In the rationale of P1, it is noticeable that the quality attribute has not been completely handled. \\

    In our design, we have not worked with states of application instances. Thus, if an application were to crash at some point, or if it would need to be shut down temporarily, etc.
    it would not be possible to save the state of an application and restore it at a later point. Maybe a simple solution for this would be to force application providers to
    implement a certain method so that the state of an application could be retrieved and stored.
