\section{Decomposition 9: UC21 (Elements/Subsystem to decompose/expand)}


\subsection{Selected architectural drivers}
    The functional drivers are:
    \begin{itemize}
        \item \emph{UC21}: Send invoice \\
    \end{itemize}


\subsection{Architectural design}
    This section describes what needs to be done to satisfy the requirements for
    this decomposition and how involved problems/obstacles are solved.

    \paragraph{UC21: Send invoice}
        Short description of the problem.\\
        Solution for the problem.

        1. The system constructs an invoice containing:
            { the provided service or product (e.g. monthly subscription fee for applications or purchased hardware),
            { the amount to be paid,
            { the date the payment is due and
            { the contact details of the primary actor (e.g. Zoomit identifier or credit card data)

                SubscriptionManager -> InvoiceManager: constructInvoice(Map<string,string>)

        2. The system sends the invoice to the third-party invoicing service.

            InvoiceManager -> InvoicingService: interface Invoices: boolean sendInvoice(Map<string,string>)
                Effect: Returns true if the ivoice was sent successfully.


\subsection{Instantiation and allocation of functionality}
    This section lists the new components which instantiate our solutions
    described in the section above. For each component we note the quality
    attribute or use case that prompted us to create it. Descriptions about
    the components can be found under chapter \ref{ch:elements-datatypes}. \\

    \begin{itemize}
        \item Component: (Relevant UC)
    \end{itemize}


\subsection{Interfaces for child modules}
    This section lists new interfaces assigned to the components defined
    in the section above. Detailed information about each interface and
    its methods can be found under chapter \ref{ch:elements-datatypes}. \\

    \subsubsection{Component}
        \begin{itemize}
            \item Interface
        \end{itemize}

\subsection{Data type definitions}
    This section lists the new data types introduced during this decomposition.

    \begin{itemize}
        \item DateTime: Represents an instant in time, typically expressed as a date and time of day.
    \end{itemize}
