\documentclass[english]{sareport}
% use the option peerreview for creating an anonymized version of your report
% E.g., \documentclass[english,peerreview]{sareport}

\usepackage[colorlinks, linkcolor=black, citecolor=black, urlcolor=black]{hyperref}
\usepackage{fontawesome}
\usepackage[normalem]{ulem}

\usepackage{graphicx}
\usepackage{rotating}
\usepackage{float}
\usepackage{enumitem}

\usepackage[T1]{fontenc}
\usepackage{lmodern}

\setlist{noitemsep} % \setlist{nosep}
\setlength{\parindent}{0pt}

% Set all authors, if your group counts 2, set third author empty \authorthree{}
% Set the groupname as well
\authorone{Monika Filipcikova (r0683254)}
\authortwo{Armin Halilovic(r0679689)}
\authorthree{}
\groupname{Filipcikova-Halilovic}
\academicyear{2016--2017}

\casename{Shared Internet Of Things Infrastructure Platform}
\phasenumber{2b}
\phasename{The Complete Architecture}

\begin{document}
\maketitle

\tableofcontents
% the following two command are necessary for obtaining the mini list of figures in the cs-view, decomposition view, deployment view and scenarios chapters
\dominilof
\fakelistoffigures

% TODO: before submitting report, remove extra notes from the template

\chapter{Architectural Decisions}\label{ch:overview}
    \input{architectural-decisions}
    \clearpage

\chapter{Client-server view (UML Component diagram)}\label{ch:client-server}
    \minilof
    \input{client-server-view}
    \clearpage

\chapter{Decomposition view (UML Component diagram)}\label{ch:decomposition}
    \minilof
    \input{decomposition-view}
    \clearpage
    % \stoplist[decomp]{lof}

\chapter{Deployment view (UML Deployment diagram)}\label{ch:deployment}
    \minilof
    \input{deployment-view}
    \clearpage

\chapter{Scenarios}\label{ch:scenarios}
    \minilof
    \input{scenarios}

% TODO: before submitting report, replace the chapter line in "exported_catalog.tex" by this line and generate the report 2 times to set all references
% TODO: before submitting report, add \newpage before \section{Interfaces} in "exported_catalog.tex"
\chapter{Element Catalog and Datatypes}\label{ch:elements-datatypes}
    % TODO: before submitting report, move this into exported_catalog
    Each method contains a short note on why the method was added (under "Created for").
    This was done to keep track of our decisions and does not mean that the methods can only
    be used for the Quality Attribute/Use Case referenced in the "Created for" note.
\input{exported_catalog}

\appendix
\chapter{Attribute-driven design documentation}\label{sec:add}
    \section{Introduction}
        This chapter contains our ADD log. First, we list the changes we
        made the ADD process so it fits our workflow better. The remaining part
        of this chapter is the ADD log. Decompositions 1 and 2 have been changed
        relative to phase 2a of this project, because we forgot about the given
        interfaces for gateways and pluggable devices and made up our own
        (but similar) interfaces instead. The decompositions have been updated
        to use the given interfaces.

    \section{Adapted ADD process}
        We left off step a ("Pick an element that needs to be decomposed") since we
        never really chose a single Element to decompose. Instead, we chose the drivers
        for each decomposition first and then looked at which elements/subsystems
        would require changes or which new elements we would need to satisfy those drivers.

        For component, interfaces, datatypes: we list the new ones, but refer
        to the plugin exported catalog for descriptions

        \subsection{Decomposition X: DRIVERS (Elements/Subsystem to decompose/expand)}
            We changed these titles to reflect the architectural drivers we chose first and then
            denote which elements/subsystems needed changes to satisfy the drivers.

        % \subsection{Selected architectural drivers}
        %     \paragraph{Rationale}
        %         The rationale for selecting and grouping architectural drivers is similar
        %         for each decomposition, so we left this paragraph out. \\
        %         The selection process goes as follows. Of the remaining quality attributes,
        %         choose those that have highest priority assigned to them.

        \subsection{New data types and Interfaces for child modules}
            For each decomposition, we have listed all new interfaces and data types
            that we added during the decomposition, but all details have been left out.
            We used the Visual Paradigm plugin provided by the SA team to generate
            the element catalog of chapter \ref{ch:elements-datatypes}. All details
            can be found in there. \\

            Also, since an ADD log was no longer a requirement for phase 2b, we
            have left out intermediary "OtherFunctionality" components and
            figures of diagrams. This was done to save time.

        \subsection{Verify and refine}
            We have skipped the verify and refine step because we chose to
            handle all chosen architectural drivers completely in every decomposition.
            We did not find this step to be useful after decompositions 1 and 2.

    \newpage
    \input{decomposition-1}
    \newpage
    \input{decomposition-2}
    \newpage
    \input{decomposition-3}
    \newpage
    \input{decomposition-4}
    \newpage
    \input{decomposition-5}
    \newpage
    \input{decomposition-6}
    \newpage
    %\input{decomposition-7}
    \newpage
    %\input{decomposition-8}
    \newpage
    %\input{decomposition-9}

\end{document}
